\documentclass[journal,12pt,twocolumn]{IEEEtran}
\usepackage[utf8]{inputenc}
 
\usepackage{tfrupee}
\usepackage{enumitem}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}

\begin{document}

\newcommand{\myvec}[1]{\ensuremath{\begin{pmatrix}#1\end{pmatrix}}}
\let\vec\mathbf

\title{Assignment 3}
\author{\textbf{Himanshu Kumar Gupta (AI21BTECH11012)}}
\maketitle
\date {May 2022}

\textbf{\textit{Ques. 7 , Ex. 16.2 , class 11 , CBSE}}

Two dice are thrown. The events A, B and C are as follows:

\begin{itemize}
\item A: getting an even number on the first die.
\item B: getting an odd number on the first die.
\item C: getting the sum of the numbers on the dice $\leq5$.
\end{itemize}
 State true or false for following: (give reason for your answer)
 
 \begin{enumerate}
\item A and B are mutually exclusive
 
\item A and B are mutually exclusive and exhaustive

\item A = B'

\item A and C are mutually exclusive

\item A and B' are mutually exclusive

\item A', B', C are mutually exclusive and exhaustive
\end{enumerate}

\textbf{\textit{Solution:}}
 \begin{enumerate}
\item \textbf{True}

We know that any number can't be both odd and even.

So,there won't be any common elements in A and B.

So,A and B are mutually exclusive.

\item \textbf{True}

Any number on dice either be odd or even,there is not any possibility other than odd and even.

So,A and B are mutually exhaustive and from $1^{st}$ part we know that A and B are mutually exclusive.

So,A and B are mutually exclusive and exhaustive.

\item \textbf{True}

We also know that if 2 sets are mutually exclusive and exhaustive,then the two are complimentary of each other.

And from $2^{nd}$ part we know that A and B are mutually exclusive and exhaustive.

So, A and B are compliment of each other i.e. A=B'

\item \textbf{False}

In C the condition is sum of both dice to be less than equal to 5.

So, first dice can have all natural number less than 4 which means have both even and odd numbers.

So, A and C have common even numbers.

That's why A and C can't be mutually exclusive.

\item \textbf{False}

from $3^{rd}$ part, A=B' 

So, A and B' can't be mutually exclusive because they are same

\item \textbf{False}

from $4^{th}$ we know that A and C are not mutually exclusive 

and from $3^{rd}$ we know that A=B'

So, B' and C are not mutually exclusive

So,A',B',C are not mutually exclusive because B' and C are not mutually exclusive

\end{enumerate}
\end{document}